CRDS Server Documentation

### 2014-07-17 docs/server_guide/build/latex/crds_server.tex
More server_guide work.
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@1563 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

% Generated by Sphinx.
\def\sphinxdocclass{report}
\documentclass[letterpaper,10pt,english]{sphinxmanual}
\usepackage[utf8]{inputenc}
\DeclareUnicodeCharacter{00A0}{\nobreakspace}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{times}
\usepackage[Bjarne]{fncychap}
\usepackage{longtable}
\usepackage{sphinx}
\usepackage{multirow}

\usepackage{enumitem}
\setlistdepth{15}

@@

\title{CRDS Server Documentation}
\date{July 16, 2014}
\release{1.1}
\author{STScI}
\newcommand{\sphinxlogo}{\includegraphics{stsci_logo.pdf}\par}
\renewcommand{\releasename}{Release}
\makeindex

@@

\def\PYG@tok@gd{\def\PYG@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
\def\PYG@tok@gu{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
\def\PYG@tok@gt{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.25,0.82}{##1}}}
\def\PYG@tok@gs{\let\PYG@bf=\textbf}
\def\PYG@tok@gr{\def\PYG@tc##1{\textcolor[rgb]{1.00,0.00,0.00}{##1}}}
\def\PYG@tok@cm{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
\def\PYG@tok@vg{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
\def\PYG@tok@m{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\def\PYG@tok@mh{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\def\PYG@tok@cs{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}\def\PYG@bc##1{\colorbox[rgb]{1.00,0.94,0.94}{##1}}}
\def\PYG@tok@ge{\let\PYG@it=\textit}
\def\PYG@tok@vc{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
\def\PYG@tok@il{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\def\PYG@tok@go{\def\PYG@tc##1{\textcolor[rgb]{0.19,0.19,0.19}{##1}}}
\def\PYG@tok@cp{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@gi{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.63,0.00}{##1}}}
\def\PYG@tok@gh{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\def\PYG@tok@ni{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.84,0.33,0.22}{##1}}}
\def\PYG@tok@nl{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.13,0.44}{##1}}}
\def\PYG@tok@nn{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.05,0.52,0.71}{##1}}}
\def\PYG@tok@no{\def\PYG@tc##1{\textcolor[rgb]{0.38,0.68,0.84}{##1}}}
\def\PYG@tok@na{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\def\PYG@tok@nb{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@nc{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.05,0.52,0.71}{##1}}}
\def\PYG@tok@nd{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.33,0.33,0.33}{##1}}}
\def\PYG@tok@ne{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@nf{\def\PYG@tc##1{\textcolor[rgb]{0.02,0.16,0.49}{##1}}}
\def\PYG@tok@si{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.44,0.63,0.82}{##1}}}
\def\PYG@tok@s2{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\def\PYG@tok@vi{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
\def\PYG@tok@nt{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.02,0.16,0.45}{##1}}}
\def\PYG@tok@nv{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
\def\PYG@tok@s1{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\def\PYG@tok@gp{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.78,0.36,0.04}{##1}}}
\def\PYG@tok@sh{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\def\PYG@tok@ow{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@sx{\def\PYG@tc##1{\textcolor[rgb]{0.78,0.36,0.04}{##1}}}
\def\PYG@tok@bp{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@c1{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
\def\PYG@tok@kc{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@c{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
\def\PYG@tok@mf{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\def\PYG@tok@err{\def\PYG@bc##1{\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{##1}}}
\def\PYG@tok@kd{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@ss{\def\PYG@tc##1{\textcolor[rgb]{0.32,0.47,0.09}{##1}}}
\def\PYG@tok@sr{\def\PYG@tc##1{\textcolor[rgb]{0.14,0.33,0.53}{##1}}}
\def\PYG@tok@mo{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\def\PYG@tok@mi{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\def\PYG@tok@kn{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@o{\def\PYG@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\def\PYG@tok@kr{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@s{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\def\PYG@tok@kp{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@w{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
\def\PYG@tok@kt{\def\PYG@tc##1{\textcolor[rgb]{0.56,0.13,0.00}{##1}}}
\def\PYG@tok@sc{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\def\PYG@tok@sb{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\def\PYG@tok@k{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\def\PYG@tok@se{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\def\PYG@tok@sd{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}

\def\PYGZbs{\char`\\}
\def\PYGZus{\char`\_}
\def\PYGZob{\char`\{}
\def\PYGZcb{\char`\}}
\def\PYGZca{\char`\^}
\def\PYGZsh{\char`\#}
\def\PYGZpc{\char`\%}
\def\PYGZdl{\char`\$}
\def\PYGZti{\char`\~}
% for compatibility with earlier versions
\def\PYGZat{@}
\def\PYGZlb{[}
\def\PYGZrb{]}
\makeatother

@@

Historical Institute contacts for the CRDS servers include:
\begin{itemize}
\item {} 
Todd Miller:    yours truly,  primary CRDS and (sole) CRDS server application developer.

@@

\section{CRDS pseudo-user and group}
\label{server_guide:crds-pseudo-user-and-group}
The CRDS servers run as the no-login user ``crds''.  The CRDS servers are maintained by getting sudo
access to the crds user and the equivalent of ``su crds'' from a normal user account.   The CRDS
crds\_server script contains the following:

\begin{Verbatim}[commandchars=\\\{\}]
ssh -A -t \$1.stsci.edu /usr/bin/sudo /bin/su - crds
\end{Verbatim}

@@

\begin{Verbatim}[commandchars=\\\{\}]
\% crds\_server plhstcrdsv1
\# crds\_server \textless{}VM-hostname\textgreater{}
\end{Verbatim}

The ssh first logs into your normal user account on the server VM, then su's you to CRDS.

@@

Members of DSB share the crdsoper group and use it to modify the CRDS server file delivery
directory described below.

@@

\begin{tabulary}{\linewidth}{|L|L|L|L|L|}
\hline
\textbf{
observatory
} & \textbf{
use
} & \textbf{
host/vm
} & \textbf{
direct port
} & \textbf{
url
}\\\hline

hst
 & 
django
 & 
localhost
 & 
8000
 & 
\href{http://localhost:8000}{http://localhost:8000}
\\\hline

hst
 & 
dev
 & 
dlhstcrdsv1
 & 
8001
 & 
\href{https://hst-crds-dev.stsci.edu}{https://hst-crds-dev.stsci.edu}
\\\hline

hst
 & 
test
 & 
tlhstcrdsv1
 & 
8001
 & 
\href{https://hst-crds-test.stsci.edu}{https://hst-crds-test.stsci.edu}
\\\hline

hst
 & 
ops
 & 
plhstcrdsv1
 & 
8001
 & 
\href{https://hst-crds.stsci.edu}{https://hst-crds.stsci.edu}
\\\hline

jwst
 & 
django
 & 
localhost
 & 
8000
 & 
\href{http://localhost:8000}{http://localhost:8000}
\\\hline

jwst
 & 
dev
 & 
dljwstcrdsv1
 & 
8001
 & 
\href{https://jwst-crds-dev.stsci.edu}{https://jwst-crds-dev.stsci.edu}
\\\hline

jwst
 & 
test
 & 
tljwstcrdsv1
 & 
8001
 & 
\href{https://jwst-crds-test.stsci.edu}{https://jwst-crds-test.stsci.edu}
\\\hline

jwst
 & 
ops
 & 
pljwstcrdsv1
 & 
8001
 & 
\href{https://jwst-crds.stsci.edu}{https://jwst-crds.stsci.edu}
\\\hline
\end{tabulary}

@@

@@

\section{/home/crds}
\label{server_guide:home-crds}
The VMs and servers share a common /home/crds directory which has potential as a single point failure.  In particular,
critical shell rc scripts (.setenv) are shared by all servers and must be updated with extreme care because
any error instantly affects all 6 servers.  Consequently, .setenv should be kept as simple as reasonably
possible.  /home/crds also houses rc\_script.

@@

@@

\subsection{Server Runtime Directories}
\label{server_guide:server-runtime-directories}
A number of subdirectories are used to store files related to running Apache, logging, or backups under
e.g. /crds/data1/dlhstcrdsv1/server.

\subsubsection{conf}
\label{server_guide:conf}
Apache config files are installed here at e.g. /crds/data1/dlhstcrdsv1/server/conf.  Files ssl.conf and httpd.conf.

\subsubsection{logs}
\label{server_guide:logs}
There are a number of Apache logs kept at e.g. /crds/data1/dlhstcrdsv1/server/logs.  These logs record requests to
Apache and stderr output from Django views not visible to end users.

>>>>

% Generated by Sphinx.
\def\sphinxdocclass{report}
\documentclass[letterpaper,10pt,english]{sphinxmanual}
\usepackage[utf8]{inputenc}
\DeclareUnicodeCharacter{00A0}{\nobreakspace}
\usepackage{cmap}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{times}
\usepackage[Bjarne]{fncychap}
\usepackage{longtable}
\usepackage{sphinx}
\usepackage{multirow}

@@

\title{CRDS Server Documentation}
\date{July 17, 2014}
\release{1.1}
\author{STScI}
\newcommand{\sphinxlogo}{\includegraphics{stsci_logo.pdf}\par}
\renewcommand{\releasename}{Release}
\makeindex

@@

\expandafter\def\csname PYG@tok@gd\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
\expandafter\def\csname PYG@tok@gu\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
\expandafter\def\csname PYG@tok@gt\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.27,0.87}{##1}}}
\expandafter\def\csname PYG@tok@gs\endcsname{\let\PYG@bf=\textbf}
\expandafter\def\csname PYG@tok@gr\endcsname{\def\PYG@tc##1{\textcolor[rgb]{1.00,0.00,0.00}{##1}}}
\expandafter\def\csname PYG@tok@cm\endcsname{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
\expandafter\def\csname PYG@tok@vg\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
\expandafter\def\csname PYG@tok@m\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\expandafter\def\csname PYG@tok@mh\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\expandafter\def\csname PYG@tok@cs\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}\def\PYG@bc##1{\setlength{\fboxsep}{0pt}\colorbox[rgb]{1.00,0.94,0.94}{\strut ##1}}}
\expandafter\def\csname PYG@tok@ge\endcsname{\let\PYG@it=\textit}
\expandafter\def\csname PYG@tok@vc\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
\expandafter\def\csname PYG@tok@il\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\expandafter\def\csname PYG@tok@go\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.20,0.20,0.20}{##1}}}
\expandafter\def\csname PYG@tok@cp\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\expandafter\def\csname PYG@tok@gi\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.63,0.00}{##1}}}
\expandafter\def\csname PYG@tok@gh\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PYG@tok@ni\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.84,0.33,0.22}{##1}}}
\expandafter\def\csname PYG@tok@nl\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.13,0.44}{##1}}}
\expandafter\def\csname PYG@tok@nn\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.05,0.52,0.71}{##1}}}
\expandafter\def\csname PYG@tok@no\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.38,0.68,0.84}{##1}}}
\expandafter\def\csname PYG@tok@na\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\expandafter\def\csname PYG@tok@nb\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\expandafter\def\csname PYG@tok@nc\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.05,0.52,0.71}{##1}}}
\expandafter\def\csname PYG@tok@nd\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.33,0.33,0.33}{##1}}}
\expandafter\def\csname PYG@tok@ne\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\expandafter\def\csname PYG@tok@nf\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.02,0.16,0.49}{##1}}}
\expandafter\def\csname PYG@tok@si\endcsname{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.44,0.63,0.82}{##1}}}
\expandafter\def\csname PYG@tok@s2\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\expandafter\def\csname PYG@tok@vi\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
\expandafter\def\csname PYG@tok@nt\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.02,0.16,0.45}{##1}}}
\expandafter\def\csname PYG@tok@nv\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.38,0.84}{##1}}}
\expandafter\def\csname PYG@tok@s1\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\expandafter\def\csname PYG@tok@gp\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.78,0.36,0.04}{##1}}}
\expandafter\def\csname PYG@tok@sh\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\expandafter\def\csname PYG@tok@ow\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\expandafter\def\csname PYG@tok@sx\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.78,0.36,0.04}{##1}}}
\expandafter\def\csname PYG@tok@bp\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\expandafter\def\csname PYG@tok@c1\endcsname{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
\expandafter\def\csname PYG@tok@kc\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\expandafter\def\csname PYG@tok@c\endcsname{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.50,0.56}{##1}}}
\expandafter\def\csname PYG@tok@mf\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\expandafter\def\csname PYG@tok@err\endcsname{\def\PYG@bc##1{\setlength{\fboxsep}{0pt}\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{\strut ##1}}}
\expandafter\def\csname PYG@tok@kd\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\expandafter\def\csname PYG@tok@ss\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.32,0.47,0.09}{##1}}}
\expandafter\def\csname PYG@tok@sr\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.14,0.33,0.53}{##1}}}
\expandafter\def\csname PYG@tok@mo\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\expandafter\def\csname PYG@tok@mi\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.13,0.50,0.31}{##1}}}
\expandafter\def\csname PYG@tok@kn\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\expandafter\def\csname PYG@tok@o\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PYG@tok@kr\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\expandafter\def\csname PYG@tok@s\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\expandafter\def\csname PYG@tok@kp\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\expandafter\def\csname PYG@tok@w\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
\expandafter\def\csname PYG@tok@kt\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.56,0.13,0.00}{##1}}}
\expandafter\def\csname PYG@tok@sc\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\expandafter\def\csname PYG@tok@sb\endcsname{\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\expandafter\def\csname PYG@tok@k\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.00,0.44,0.13}{##1}}}
\expandafter\def\csname PYG@tok@se\endcsname{\let\PYG@bf=\textbf\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}
\expandafter\def\csname PYG@tok@sd\endcsname{\let\PYG@it=\textit\def\PYG@tc##1{\textcolor[rgb]{0.25,0.44,0.63}{##1}}}

\def\PYGZbs{\char`\\}
\def\PYGZus{\char`\_}
\def\PYGZob{\char`\{}
\def\PYGZcb{\char`\}}
\def\PYGZca{\char`\^}
\def\PYGZam{\char`\&}
\def\PYGZlt{\char`\<}
\def\PYGZgt{\char`\>}
\def\PYGZsh{\char`\#}
\def\PYGZpc{\char`\%}
\def\PYGZdl{\char`\$}
\def\PYGZhy{\char`\-}
\def\PYGZsq{\char`\'}
\def\PYGZdq{\char`\"}
\def\PYGZti{\char`\~}
% for compatibility with earlier versions
\def\PYGZat{@}
\def\PYGZlb{[}
\def\PYGZrb{]}
\makeatother

@@

Historical Institute contacts for the CRDS servers include:
\begin{itemize}
\item {} 
Todd Miller:    primary CRDS and CRDS server application developer.

@@

\section{CRDS pseudo-user and group}
\label{server_guide:crds-pseudo-user-and-group}
The CRDS servers run as the no-login user ``crds''.  The CRDS  crds\_server script contains the following:

\begin{Verbatim}[commandchars=\\\{\}]
\PYGZpc{} ssh \PYGZhy{}A \PYGZhy{}t \PYGZdl{}1.stsci.edu /usr/bin/sudo /bin/su \PYGZhy{} crds
\end{Verbatim}

@@

\begin{Verbatim}[commandchars=\\\{\}]
\PYGZpc{} crds\PYGZus{}server plhstcrdsv1
\PYGZsh{} crds\PYGZus{}server \PYGZlt{}VM\PYGZhy{}hostname\PYGZgt{}
\end{Verbatim}

The ssh first logs into your normal user account on the server VM, then su's you to CRDS.   It is not possible
to directly login to the crds user.

@@

Members of DSB share the crdsoper group and use it to modify the CRDS server file delivery
directory described below or copy files directly to their ingest directories.

@@

\begin{tabulary}{\linewidth}{|L|L|L|L|L|}
\hline
\textsf{\relax 
observatory
} & \textsf{\relax 
use
} & \textsf{\relax 
host/vm
} & \textsf{\relax 
direct port
} & \textsf{\relax 
url
}\\
\hline
hst
 & 
django
 & 
localhost
 & 
8000
 & 
\href{http://localhost:8000}{http://localhost:8000}
\\

hst
 & 
dev
 & 
dlhstcrdsv1
 & 
8001
 & 
\href{https://hst-crds-dev.stsci.edu}{https://hst-crds-dev.stsci.edu}
\\

hst
 & 
test
 & 
tlhstcrdsv1
 & 
8001
 & 
\href{https://hst-crds-test.stsci.edu}{https://hst-crds-test.stsci.edu}
\\

hst
 & 
ops
 & 
plhstcrdsv1
 & 
8001
 & 
\href{https://hst-crds.stsci.edu}{https://hst-crds.stsci.edu}
\\

jwst
 & 
django
 & 
localhost
 & 
8000
 & 
\href{http://localhost:8000}{http://localhost:8000}
\\

jwst
 & 
dev
 & 
dljwstcrdsv1
 & 
8001
 & 
\href{https://jwst-crds-dev.stsci.edu}{https://jwst-crds-dev.stsci.edu}
\\

jwst
 & 
test
 & 
tljwstcrdsv1
 & 
8001
 & 
\href{https://jwst-crds-test.stsci.edu}{https://jwst-crds-test.stsci.edu}
\\

jwst
 & 
ops
 & 
pljwstcrdsv1
 & 
8001
 & 
\href{https://jwst-crds.stsci.edu}{https://jwst-crds.stsci.edu}
\\
\hline\end{tabulary}

@@

\chapter{Mailing Lists}
\label{server_guide:mailing-lists}
The following CRDS mailing lists are defined on behalf of CRDS:

\begin{tabulary}{\linewidth}{|L|L|L|}
\hline
\textsf{\relax 
mailing list
} & \textsf{\relax 
moderator
} & \textsf{\relax 
purpose
}\\
\hline
\href{mailto:crds@stsci.edu}{crds@stsci.edu}
 & 
mcmaster
 & 
comm between INS and CRDS team, also accidental use
\\

\href{mailto:crds\_team@stsci.edu}{crds\_team@stsci.edu}
 & 
mcmaster
 & 
comm within CRDS delivery team, DSB, archive, pipelines
\\

\href{mailto:crds\_datamng@stsci.edu}{crds\_datamng@stsci.edu}
 & 
mcmaster
 & 
common destination for affected datasets output
\\

\href{mailto:crds-servers@stsci.edu}{crds-servers@stsci.edu}
 & 
jmiller
 & 
little used,  new source address for affected datasets,  server details + news
\\

\href{mailto:crds\_hst\_ops\_reprocessing@stsci.edu}{crds\_hst\_ops\_reprocessing@stsci.edu}
 & 
jmiller
 & 
affected datasets output list, hst ops
\\

\href{mailto:crds\_hst\_test\_reprocessing@stsci.edu}{crds\_hst\_test\_reprocessing@stsci.edu}
 & 
jmiller
 & 
affected datasets output list, hst test
\\

\href{mailto:crds\_jwst\_ops\_reprocessing@stsci.edu}{crds\_jwst\_ops\_reprocessing@stsci.edu}
 & 
jmiller
 & 
affected datasets output list, jwst ops
\\

\href{mailto:crds\_jwst\_test\_reprocessing@stsci.edu}{crds\_jwst\_test\_reprocessing@stsci.edu}
 & 
jmiller
 & 
affected datasets output list, jwst test
\\
\hline\end{tabulary}

These are all closed lists.  Most critical are crds\_team and crds\_datamng.   The reprocessing lists are intended and/or used to drive
automated systems so be careful with traffic on those.

@@

\section{Cross-Server Shared Home (/home/crds)}
\label{server_guide:cross-server-shared-home-home-crds}
The VMs and servers share a common /home/crds directory which has potential as a single point failure.  In particular,
critical shell rc scripts (.setenv) are shared by all servers and must be updated with extreme care because
any error instantly affects all 6 servers.

@@

The RC scripts are version controlled with the server source code in the directory ``hosts'' under the names dot\_setenv
and rc\_script.

\subsection{.setenv}
\label{server_guide:setenv}
The CRDS user runs under /bin/tcsh and executes .setenv for CRDS-server specific initializations.   Note that
\$HOME/.setenv is shared across all CRDS servers and should be modified with extreme caution.   The environment
variables defined to differentiate the 6 CRDS servers are,  for example for JWST DEV:

\begin{Verbatim}[commandchars=\\\{\}]
CRDS\PYGZus{}PROJECT        jwst
CRDS\PYGZus{}USECASE        dev
CRDS\PYGZus{}SERVER         dljwstcrdsv1
CRDS                /crds/data1/dljwstcrdsv1
PATH                /crds/data1/dljwstcrdsv1/CRDS\PYGZus{}server/host   /crds/data1/dljwstcrdsv1/crds\PYGZus{}stacks/crds\PYGZus{}11/bin
CRDS\PYGZus{}STACK          /crds/data1/dljwstcrdsv1/crds\PYGZus{}stacks/crds\PYGZus{}11
CRDS\PYGZus{}AFFECTED...    jmiller@stsci.edu eisenhamer@stsci.edu
CRDS\PYGZus{}IFS            /ifs/crds/jwst/dev
CRDS\PYGZus{}FILE\PYGZus{}CACHE     /ifs/crds/jwst/dev/file\PYGZus{}cache
CRDS\PYGZus{}SERVER\PYGZus{}FILES   /ifs/crds/jwst/dev/server\PYGZus{}files
META\PYGZus{}PREFIX         /crds/data1/dljwstcrdsv1/crds\PYGZus{}stacks/crds\PYGZus{}11
\end{Verbatim}

Additional environment variables, particularly those related to server installation, are defined in
\$\{CRDS\}/CRDS\_server/env.csh.

META\_PREFIX is roughly equivalent to /usr/local,  the common value passed to --prefix in ./configure,  etc.,
for building the server Python stack.

\subsection{.alias}
\label{server_guide:alias}
CRDS augments the standard .alias file with these aliases for moving around the file system:

\begin{Verbatim}[commandchars=\\\{\}]
\PYGZsh{}  Source code areas
alias crds       \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZcb{}/CRDS\PYGZdq{}
alias server     \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZcb{}/CRDS\PYGZus{}server\PYGZdq{}
alias stack      \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZus{}STACK\PYGZcb{}\PYGZdq{}
alias installer \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZcb{}/crds\PYGZus{}stacks/installer3/build\PYGZdq{}

\PYGZsh{} Server maintenance areas
alias logs       \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZcb{}/server/logs\PYGZdq{}
alias backups    \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZcb{}/server/db\PYGZus{}backups\PYGZdq{}

\PYGZsh{} CRDS code area
alias libpython  \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZcb{}/python/lib/python\PYGZdq{}

\PYGZsh{} Server working data files areas
alias deliveries \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZus{}SERVER\PYGZus{}FILES\PYGZcb{}/deliveries\PYGZdq{}
alias catalogs   \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZus{}SERVER\PYGZus{}FILES\PYGZcb{}/catalogs\PYGZdq{}
alias ingest     \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZus{}SERVER\PYGZus{}FILES\PYGZcb{}/ingest\PYGZdq{}
alias file\PYGZus{}cache \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZus{}FILE\PYGZus{}CACHE\PYGZcb{}\PYGZdq{}

\PYGZsh{} Isilon and VM file systems
alias ifs        \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZus{}IFS\PYGZcb{}\PYGZdq{}
alias data1      \PYGZdq{}cd \PYGZdl{}\PYGZob{}CRDS\PYGZcb{}\PYGZdq{}
\end{Verbatim}

\subsection{rc\_script}
\label{server_guide:rc-script}
The /home/crds/rc\_script is executed to restart the servers,  or shut them down,  whenever the server is rebooted.

@@

\subsection{server runtime directory}
\label{server_guide:server-runtime-directory}
A number of subdirectories are used to store files related to running Apache, logging, or backups under
e.g. /crds/data1/dlhstcrdsv1/server.

\subsubsection{conf subdirectory}
\label{server_guide:conf-subdirectory}
Apache config files are installed here at e.g. /crds/data1/dlhstcrdsv1/server/conf.  Files ssl.conf and httpd.conf.
